\textsf{Are large language models superhuman chemists?}

### 2024-10-30 src/tex/appendix.tex
fix some crefs

In addition, as shown in \Cref{fig:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows a balanced distribution of the required skills in the \chembench corpus. \Cref{tab:cb_skillset} shows an example question for each skill category.

@@

In analyzing the performance of state-of-the-art models on the \chembench corpus, we identified several chemical topics where the models consistently struggled to provide correct answers. The following table \cref{tab:chembench_corpus_models_failed_topic} presents examples of challenging questions across different chemical domains, highlighting specific areas where current models need improvement

@@

An interesting observation is the significant impact of chemical preference tasks on \GPTFour's scores. A detailed breakdown of overall accuracy into scores on different skills and difficulty levels is provided in \Cref{table:performance_table} and \Cref{tab:performance_table_human_subset} for \chembench corpus and the \chembenchmini subset, respectively.

>>>>

In addition, as shown in \Cref{fig:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows a balanced distribution of the required skills in the \chembench corpus. \Cref{fig:cb_skillset} shows an example question for each skill category.

@@

In analyzing the performance of state-of-the-art models on the \chembench corpus, we identified several chemical topics where the models consistently struggled to provide correct answers. The following \Cref{tab:chembench_corpus_cognitive} presents examples of challenging questions across different chemical domains, highlighting specific areas where current models need improvement

@@

An interesting observation is the significant impact of chemical preference tasks on \GPTFour's scores. A detailed breakdown of overall accuracy into scores on different skills and difficulty levels is provided in \Cref{tab:performance_table} and \Cref{tab:performance_table_human_subset} for \chembench corpus and the \chembenchmini subset, respectively.
